---
title: "Rgram-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tour to Rgram package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Rgram)
```

This document introduces Rgram and shows how to use the package. 

## Introduction to Rgram 

Images form a significant part of the data in today's world. Whether you want to enhance your poorly-lit profile picture or analyze satellite images, filters are your best friends.Rgram aims to help you to create four filters for your image: 


- `flipping`: This function can be used to flip the image horizontally in black and white.

- `greyscale`: This function can be used to convert a color image into a greyscale image.  

- `padding`: This function can be used to add padding to the the borders of an image. 

- `rotate`: This function can be used to rotate an image by the specified number of degrees. 


## Data: An image to be called using 'library(imager)' or 'library(png)' 

To call/read your input image you need to load two libraries: imager and png. 

```{r}
library(imager)
library(png)
```

## Examples 


#### 'greyscale' function 


```
grayscale("https://raw.githubusercontent.com/UBC-MDS/Rgram/master/tests/testthat/test_images/grayscale/sample.jpg") %>% plot()
```


#### 'rotate' function 


```
rotate("https://raw.githubusercontent.com/UBC-MDS/Rgram/master/tests/testthat/test_images/rotate/sample.jpg", 60) %>% 
  plot()
```


#### 'padding' function 


```
padding("https://raw.githubusercontent.com/UBC-MDS/Rgram/master/tests/testthat/test_images/padding/sample.jpg", 20) %>% 
  plot()
```
